### 2015-12-14 ch05-initvals/InitialValuesPaper.tex
initval: meas figures/table on own pages

To measure the transfer function, the \BK{} 1613 Filter was excited by a signal $r(t)$ and both its input $u(t)$ and output $y(t)$ were measured as shown in \figref{fig:measurementSetup}.
The output $y(t)$, however, was disturbed by a noise generator that added white noise over the frequency range $[\mathrm{DC}, 20\unit{kHz}]$.
The excitation signal $r(t)$ was white random noise with a standard deviation $\sigma_r = 0.25 \unit{V}$, consisting of $N_S = 8\,192$ samples, and sampled at $92 \unit{kHz}$.
The same noise sequence was repeated $N_R = 100$ times in succession, such that a non-parametric estimate of the noise could be obtained and the performance of the methods could be gauged over these different repetitions.
To distinguish the different repetitions, we denote the $r^{\text{th}}$ repetition of the $u$ signal as $u^{[r]}(t)$ (and similarly for $y(t)$).
The signal generation and acquisition was by means of a National Instruments Elvis II, using the respective \code{AO} and \code{AI} pins on the breadboard, which were wired to BNC connectors.
Although acquisition and generation were synchronized, there was a small delay $\tau = 9\unit{\mu s}$ between the acquisition of the input $u(t)$ and the output $y(t)$.
The output spectrum $Y(\omega)$ was multiplied by $\exp\left(-j\omega\tau \right)$ such that the delay-compensated $y(t)$ could be obtained using the inverse DFT.

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\onecolumnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \setlength{\figurewidth}{0.75\onecolumnwidth}
  \input{\thisDir/fig/CostFunctionsMLE-measurement.tikz}
  \caption[Cost function values over the different measurements.]{Cost function values $V(\theta)$ obtained during the different realizations of the measurement.
  The bottom plot shows a zoom of the top plot.
  For each method, the inter-quartile range~\legref{leg:costMeasurements:best:iqr}, median~\legref{leg:costMeasurements:best:median} and individual values~\legref{leg:costMeasurements:best:data} are shown.
  This implies that a lower (local) minimum of the cost function can be attained using these smoothing techniques.}
  \label{fig:costMeasurements}
\end{figure}

\begin{table}
  \centering
  \caption{Observed percentiles of the cost function $V(\model{\bullet}$).}
% \input{\thisDir/table1.tex}
\pgfplotstabletypeset[precision=0]{
method            P000     P025     P050      P075       P100   
\model{VXI}       4354.83  4442.31  4493.52   4706.61    9633.53
\model{exist}     4345.3   4525.82  8740.54  12413.3    29236.5
\model{trunc}     4335.68  4476.29  4841.74   8130.28   88308.1
\model{RFIR}      4328.93  4422.11  4468.8    4716.46    9606.54
\model{best}      4328.93  4414.87  4457.91   4644.07    8569.93 
}
  \label{tbl:costMeasurements}
\end{table}

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\onecolumnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \setlength{\figurewidth}{0.75\onecolumnwidth}
  \input{\thisDir/fig/meas-validation.tikz}
  \caption[Validation cost of the different measurements.]{Validation of the measured models. 
  For each method, the distance \eqref{eq:measurementCriterion} between the estimates and $\model{VXI}$ is shown~\legref{leg:validationMeasurements:best:data} together with the median~\legref{leg:validationMeasurements:best:median} and inter-quartile range~\legref{leg:validationMeasurements:best:iqr}.
  $\norm{G_{\mathrm{VXI}}}$\legref{leg:validationMeasurements:H2Norm} is shown as a reference.
  The bottom plot shows a zoom of the top plot.
  The proposed methods yield models that are closer to $\model{VXI}$ than the existing $\model{exist}$.
  The results are in line with the values of the cost function in \figref{fig:costMeasurements}.}
  \label{fig:validationMeasurements}
\end{figure}
\begin{table}
  \centering
  \caption{Observed percentiles of the validation distance $\norm{\model{\bullet}-G_{\mathrm{VXI}}}$.}
% \input{\thisDir/table2.tex}

>>>>

To measure the transfer function, the \BK{} 1613 Filter was excited by a signal $r(t)$ and both its input $u(t)$ and output $y(t)$ were measured as shown in \figref{fig:measurementSetup}.
The output $y(t)$, however, was disturbed by a noise generator that added white noise over the frequency range $[\mathrm{DC}, 20\unit{kHz}]$.
The excitation signal $r(t)$ was white random noise with a standard deviation $\sigma_r = 0.25 \unit{V}$, consisting of $N_S = 8\,192$ samples, and sampled at $92 \unit{kHz}$.
The same noise sequence was repeated $N_R = 100$ times in succession, such that a non-parametric estimate of the noise could be obtained and the performance of the methods could be gauged over these different repetitions.
To distinguish the different repetitions, we denote the $r^{\text{th}}$ repetition of the $u$ signal as $u^{[r]}(t)$ (and similarly for $y(t)$).
The signal generation and acquisition was by means of a National Instruments Elvis II, using the respective \code{AO} and \code{AI} pins on the breadboard, which were wired to BNC connectors.
Although acquisition and generation were synchronized, there was a small delay $\tau = 9\unit{\mu s}$ between the acquisition of the input $u(t)$ and the output $y(t)$.
The output spectrum $Y(\omega)$ was multiplied by $\exp\left(-j\omega\tau \right)$ such that the delay-compensated $y(t)$ could be obtained using the \gls{IDFT}.

@@

\begin{figure}[p]
  \centering
  \setlength{\figurewidth}{0.85\onecolumnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \setlength{\figurewidth}{0.75\onecolumnwidth}
  \input{\thisDir/fig/CostFunctionsMLE-measurement.tikz}
  \caption[Cost function values over the different measurements.]{Cost function values $V(\theta)$ obtained during the different realizations of the measurement.
  The bottom plot shows a zoom of the top plot.
  For each method, the inter-quartile range~\legref{leg:costMeasurements:best:iqr}, median~\legref{leg:costMeasurements:best:median} and individual values~\legref{leg:costMeasurements:best:data} are shown.
  This implies that a lower (local) minimum of the cost function can be attained using these smoothing techniques.}
  \label{fig:costMeasurements}
\end{figure}

\begin{table}[p]
  \centering
  \caption{Observed percentiles of the cost function $V(\model{\bullet}$).}
% \input{\thisDir/table1.tex}
\pgfplotstabletypeset[precision=0]{
method            P000     P025     P050      P075       P100   
\model{VXI}       4354.83  4442.31  4493.52   4706.61    9633.53
\model{exist}     4345.3   4525.82  8740.54  12413.3    29236.5
\model{trunc}     4335.68  4476.29  4841.74   8130.28   88308.1
\model{RFIR}      4328.93  4422.11  4468.8    4716.46    9606.54
\model{best}      4328.93  4414.87  4457.91   4644.07    8569.93 
}
  \label{tbl:costMeasurements}
\end{table}

@@

\begin{figure}[p]
  \centering
  \setlength{\figurewidth}{0.85\onecolumnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \setlength{\figurewidth}{0.75\onecolumnwidth}
  \input{\thisDir/fig/meas-validation.tikz}
  \caption[Validation cost of the different measurements.]{Validation of the measured models. 
  For each method, the distance \eqref{eq:measurementCriterion} between the estimates and $\model{VXI}$ is shown~\legref{leg:validationMeasurements:best:data} together with the median~\legref{leg:validationMeasurements:best:median} and inter-quartile range~\legref{leg:validationMeasurements:best:iqr}.
  $\norm{G_{\mathrm{VXI}}}$\legref{leg:validationMeasurements:H2Norm} is shown as a reference.
  The bottom plot shows a zoom of the top plot.
  The proposed methods yield models that are closer to $\model{VXI}$ than the existing $\model{exist}$.
  The results are in line with the values of the cost function in \figref{fig:costMeasurements}.}
  \label{fig:validationMeasurements}
\end{figure}
\begin{table}[p]
  \centering
  \caption{Observed percentiles of the validation distance $\norm{\model{\bullet}-G_{\mathrm{VXI}}}$.}
% \input{\thisDir/table2.tex}
